Non-negligible Effects of Electronic Polarization at Negatively Charged Membranes with Ions

### 2019-05-09 Manuscript/manuscript.tex
Added the populations of calcium at PC&PS:various_moieties into table 4
Convert Table 4 with populations of bound Ca2+ in membrane to a new plot, which is a part of Fig 10, which also contains lipid stoichiometries.

%In contrast, the combination of NMR experiments 
%and MD simulations with the same model, CHARMM36, but without the correction for calcium binding
%also reveal long-lived interactions of \ce{Ca^{2+}} with \ce{PO4} groups. \cite{hallock18}
%Although the ratios of the life times of coordination follow the same trends as in our work,
%the lengths of simulation trajectories are insufficient 
%to yield converged results in this aspect (see SI and Refs.~\cite{catte16, melcr18, NMRlipidsIV}). 
\begin{table}[tb!] 
\centering
\caption{%Bulk concentrations, $C _{Ca}$, and buffer concentrations, $C' _{Ca}$, of Ca$^{2+}$;
  % relative surface excess of calcium with respect to water ($\Gamma_{Ca}^{\rm water}$); 
  % and
  Percentages of the population of bound Ca$^{2+}$ to various lipid moieties in a pure POPC bilayer with 350 mM CaCl$_2$
  and in a POPC:POPS (5:1) mixture with 409 mM CaCl$_2$. The threshold for counting a contact was set to $0.3\,\mathrm{nm}$, which encompasses the
  first peak of the radial distribution function between the cations and the oxygen atoms of the lipids. 
  \label{tab:binding}} 
\begin{tabular}{ l | c c } 
 exclusive interacting moiety &  \multicolumn{2}{c}{percentage of bound \ce{Ca^{2+}} } \\
%	\hline
%	$C _{Ca}\,/\,\mathrm{mM}$  &  $240\pm 10 $  &  $280\pm 10 $  \\
%	$C'_{Ca}\,/\,\mathrm{mM}$  &  $400\pm 10 $  &  $350\pm 10 $  \\
%	$\Gamma_{Ca}^{\rm water}\, / \,\mathrm{nm}^{-2}$  &  $0.24 \pm 0.01 $  &  $0.06 \pm 0.01 $  \\
%	\hline
%                             &  \multicolumn{2}{c}{ } \\
                             &  5\,POPC:1\,POPS &  POPC   \\
    \hline
    \textbf{PC}              &   59   &  100   \\
	     PO$_4$    in PC &   41   &   67   \\
	     carbonyls in PC &   <1   &   ~1   \\
    \hline
    \textbf{PS}              &    8   &        \\ 
	     PO$_4$  in PS   &    2   &        \\
	     COO$^-$ in PS   &    4   &        \\
	     carbonyls in PS &   <1   &        \\
    \hline
    \textbf{both PC and PS}  &   33   &        \\
  \end{tabular} \\
  %\todo{I have commented out the surface excess values (available in text) and concentrations (now in caption) from the table.} \\
  %\todo{I do not understand the numbers for different moieties. Are these probabilities that the calcium binds only to these moieties and
  %  nothing else? In total, 41 \% binds to PS lipids, but only 2 \% and 4 \% to phosphates and COO$^-$, respectively? Where do the rest bind?
  %  I think that we should show the total probabilities to bind to different moieties.}
\end{table}

\begin{figure}[tb!] 
  \centering 
  \includegraphics[width=\figwidth]{../img/stoichiometry_CaCl2_comparison_Ecc-lipids_PC-vs-PCPS.pdf} \\ 
  \caption{\label{fig:cacl_complexes} 
    Relative probabilities of \ce{Ca^{2+}} ions to coordinate with a certain number of lipids
    in pure POPC bilayer with 350 mM CaCl$_2$ and in POPC:POPS (5:1) mixture with 400 mM CaCl$_2$.  
    Analysis was done for both systems by considering all lipids (blue and violet) and
    for POPC:POPS (5:1) mixture also by considering POPC and POPS lipids separately (green and orange).
    %All lipids were taken into account with the exception of the complexes in light green and orange, 
    %for which we counted only contacts with POPC resp POPS from the mixed 5\,PC:1\,PS negatively charged bilayer. 
    %The calculated probabilities of the calcium-lipid complexes also reflect only POPC (light green) resp POPS (orange). 
    % Probabilities were taken from simulations with comparable bulk concentrations of calcium around 250~mM. 
    Clusters of four or more lipids were not observed in either membrane.
    The threshold for counting coordinated lipids in a complex with \ce{Ca^{2+}} was set to $0.3\,\mathrm{nm}$, 
    as the distance between the cation and the oxygen atoms of the lipids. 
    Previously published simulation data \cite{melcr18} for pure POPC bilayers were taken directly from \cite{ECC-POPC_nacl_cacl2_files}. 
  }
\end{figure}

>>>>

%In contrast, the combination of NMR experiments 
%and MD simulations with the same model, CHARMM36, but without the correction for calcium binding
%also reveal long-lived interactions of \ce{Ca^{2+}} with \ce{PO4} groups. \cite{hallock18}
%Although the ratios of the life times of coordination follow the same trends as in our work,
%the lengths of simulation trajectories are insufficient 
%to yield converged results in this aspect (see SI and Refs.~\cite{catte16, melcr18, NMRlipidsIV}).

\begin{figure}[tb!] 
  \centering 
  \includegraphics[width=\figwidthsmall]{../img/bound_ca_populations.pdf} 
  \includegraphics[width=\figwidthsmall]{../img/stoichiometry_CaCl2_comparison_Ecc-lipids_PC-vs-PCPS.pdf} \\ 
  \caption{ \label{fig:cacl_complexes} 
  Left: Percentages of the population of bound Ca$^{2+}$ 
in exclusive contact with various lipid moieties 
in a POPC:POPS (5:1) bilayer with 409 mM CaCl$_2$. 
For comparison, in a pure POPC bilayer with 350 mM CaCl$_2$, 
67\% of bound \ce{Ca^{2+}} is exclusively in contact with \ce{PO_4} group. \cite{melcr18} \\
    Right: Relative probabilities of \ce{Ca^{2+}} ions to coordinate with a certain number of lipids
    in pure POPC bilayer with 350 mM CaCl$_2$ and in POPC:POPS (5:1) mixture with 400 mM CaCl$_2$.  
    Analysis was done for both systems by considering all lipids (blue and violet) and
    for POPC:POPS (5:1) mixture also by considering POPC and POPS lipids separately (green and orange). \\
    %All lipids were taken into account with the exception of the complexes in light green and orange, 
    %for which we counted only contacts with POPC resp POPS from the mixed 5\,PC:1\,PS negatively charged bilayer. 
    %The calculated probabilities of the calcium-lipid complexes also reflect only POPC (light green) resp POPS (orange). 
    % Probabilities were taken from simulations with comparable bulk concentrations of calcium around 250~mM. 
    Clusters of four or more lipids were not observed in either membrane.
    The threshold for counting coordinated lipids in a complex with \ce{Ca^{2+}} was set to $0.3\,\mathrm{nm}$, 
    as the distance between the cation and the oxygen atoms of the lipids. 
    Previously published simulation data \cite{melcr18} for pure POPC bilayers were taken directly from \cite{ECC-POPC_nacl_cacl2_files}. 
  }
\end{figure}
